Comparing vector-based and Bayesian memory models using large-scale datasets:\protect\\User-generated hashtag and tag prediction on Twitter and StackOverflow

### 2016-06-12 writeups/psycMethodsResponse2/response.tex

FIXME: Add text

\end{solution}

\question Lesser concern: Per Rev 3, para 5 and 7, please incorporate any additional relevant literature (but do not limit yourself to Rev 3 citations; check out what is current and relevant given this quickly changing phenomenon and research area).

\begin{solution}
Added a paragraph in the background section to discuss the types of hashtag-prediction models that were mentioned by Rev 3:

fixme: add text
\end{solution}

@@

\question The counterintuitive results are also intriguing (such as the finding that larger training corpora lowered performance for the random permutations models). However, one factor to consider is that RP models depend on the approximate orthogonality of the random projections (the environment vectors for Beagle). As the number of words increases, this will tend to oversaturate the space, and commonly leads to decreased performance. One standard approach here is to scale the dimensionality of the representations as the training set and vocabulary sizes increase. It would be interesting to see if the performance still leveled off if you increased the dimensionality with the corpus size.

\begin{solution}
Addressed this by including in the paper the work that looked at model accuracy vs. corpus size and number of rows in the random permutation model.
The text for the section has been previously included in this document.
\end{solution}

\question A number of works have considered the large scale dynamics of hashtag use (e.g. ``\#Bigbirds Never Die: Understanding Social Dynamics of Emergent Hashtags'', 2013), while other work has looked specifically at the impact of tags used by a user's local network connections (``We know what @you \#tag: does the dual role affect hashtag adoption?'', 2012). There is an extensive literature exploring how user features including demographics (e.g. ``User Conditional Hashtag Prediction for Images'', 2015), prior posts, time of day, mood, etc. The relationship between this literature and the work presented in the paper needs to be discussed thoroughly.

\begin{solution}
Addressed this by reviewing the literature and including a paragraph in the background section.
The text for this section has been previously included in this document.
\end{solution}

### 2016-06-12 writeups/psycMethods/psycMethods.tex
foo

Other successful models have shown that higher-level processes such as a user's goals for picking a hashtag, demographics, and specifics about how a hashtag has been used in the past can also influence hashtag use.
\textcite{lin2013bigbirds} showed that there are at least two distinct use cases for hashtags on Twitter: to mark the content (traditional tagging) and to contribute to a specific community that has created a hashtag.
\textcite{yang2012we} found that demographics such as gender, age, and location can influence a user's selected hashtag.
\textcite{denton2015user} found that the growth and lifetime of a hashtag can be influenced by factors such as how often the hashtag was retweeted (and by how many unique users), and the number of followers for a user that used a particular hashtag.
These types of goal-related features, demographic information, and higher-level attributes of previous hashtag use were not directly included in the declarative memory models that were tested for this research.
They were not included because it would be difficult (although likely not impossible) to fit these features into a modeling framework that is constrained to use only declarative memory processes,
and this research focused on measuring differences in model accuracy for two declarative memory models.
Nonetheless many of these higher-level features may indirectly influence a declarative memory model by influencing the specific tags that a user has chosen in the past,
which in turn boosts base-level activation for these previously-chosen tags, which in turn makes it more likely that they are chosen in the future.

>>>>

Other successful models have shown that higher-level processes such as a user's goals for picking a hashtag, demographics, and specifics about how a hashtag has been used in the past can also influence hashtag use.
\textcite{lin2013bigbirds} showed that there are at least two distinct use cases for hashtags on Twitter: to mark the content (traditional tagging) and to contribute to a specific community that has created a hashtag.
\textcite{yang2012we} found that demographics such as gender, age, and location can influence a user's selected hashtag.
\textcite{denton2015user} found that the growth and lifetime of a hashtag can be influenced by factors such as how often the hashtag was retweeted and the number of followers for a user that used a particular hashtag.
These types of goal-related features, demographic information, and higher-level attributes of previous hashtag use were not directly included in the declarative memory models that were tested for this research.
They were not included because it would be difficult (although likely not impossible) to fit these features into a modeling framework that is constrained to use only declarative memory processes,
and this research focused on measuring differences in model accuracy for two declarative memory models.
Nonetheless many of these higher-level features may indirectly influence a declarative memory model by influencing the specific tags that a user has chosen in the past,
which in turn boosts base-level activation for these previously-chosen tags, which in turn makes it more likely that they are chosen in the future.
